\section*{Instructions}

\begin{notebox}
Homework 1 covers the basic algorithms in Machine Learning, including linear regression and logistic regression. Each problem includes some short derivation questions to help you go through the necessary knowledge to complete the following coding task. Read through the Instructions below before you start working on the homework.
\end{notebox}

\begin{itemize}
\item \textbf{Collaboration Policy:} Collaboration on solving the homework is allowed, after you have thought about the problems on your own. It is also OK to get clarification (but not solutions) from books or online resources, again after you have thought about the problems on your own. There are two requirements: first, cite your collaborators fully and completely (e.g., ``Jane explained to me what is asked in Question 2.1''). Second, write your solution {\em independently}: close the book and all of your notes, and send collaborators out of the room, so that the solution comes from you only. 

\item\textbf{Late Submission Policy:} The submission of an assignment made past the deadline will get 70\% of the credits. Any assignment submitted more than 3 days past the deadline will get zero credit.

\item\textbf{Submission Policy} 

\begin{itemize}
\item \textbf{Written problems submission:} For written problems such as short answer, multiple choice, derivations, proofs, or plots, please write your solution in the LaTeX files provided in the assignment and submit in a PDF form. Put your answers in the question boxes (between \texttt{\textbackslash begin\{soln\}} and \texttt{\textbackslash end\{soln\}}) below each problem. \textbf{Handwritten solutions are not accepted and will receive zero credit.} Regrade requests can be made, however this gives the TA the opportunity to regrade your entire paper, meaning if additional mistakes are found then points will be deducted. Please upload the written problems via the Eds platform.

\item \textbf{Code submission:} All code must be submitted under the specific instruction given in the problem. We will be using the Edstem platform to auto-grade your code. \textbf{If you do not submit your code there, you will not receive any credit for your assignment.} The Edstem platform will auto-detect the possible plagiarism. Please make sure you familiarize yourself with the academic integrity information for this course.

\end{itemize}

% \item \textbf{Materials:} Download from autolab the tar file (``Download handout"). The tar file will contain all the data that you will need in order to complete this assignment.

\end{itemize}